The framing of active school travel in Ontario, Canada as a health and built environment issue

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Fixed an error in the references that prevented the Rmd file AST-framing-Ontario from knitting

```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the municipal or regional government documents."}
ggraph(municipal_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r consortia-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the transportation consortia documents."}
ggraph(consortium_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "red", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r school-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the school board documents."}
ggraph(school_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "orange", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined)."}
ggraph(policy_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "purple", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers."}
ggraph(academic_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

kbl(text_tbl) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  column_spec(3, width = "30em")
```

@@

```{r corpus-lda-model, include=FALSE}
municipal_lda <- LDA(municipal_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)

@@

```{r policy-terms, echo=FALSE}
policy_top_terms <- policy_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

@@

```{r academic-terms, echo=FALSE, cache=TRUE}

@@

Finally, we conduct topic modelling to examine the different topics found in the policy and academic corpora. We focus on the policy corpus, instead of individually assessing the municipal, school, and consortia documents, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario. To determine the number of discrete topics in each corpus, we use the _ldatuning_ package. We then use the `LDA` function from the _topicmodels_ package to estimate an LDA model for each group of documents. The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics. After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified. We experimented with the model by adjusting the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap. Figures \ref{fig: policy-terms} and \ref{fig: academic-terms} present the main terms that are associated with the topics found in each corpus.

>>>>

```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:city-visual}Most common bigrams found in the municipal or regional government documents."}
ggraph(municipal_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r consortia-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents."}
ggraph(consortium_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "red", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r school-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:school-visual}Most common bigrams found in the school board documents."}
ggraph(school_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "orange", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:policy-visual}Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined)."}
ggraph(policy_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "purple", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:academic-visual}Most common bigrams found in the academic papers."}
ggraph(academic_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

@@

kbl(text_tbl,
    booktabs = TRUE,
    caption = "\\label{tab:policy-concordance}CAPTION THIS TABLE") %>%
  kable_paper(full_width = F) %>%
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, bold = T) %>%
  column_spec(3, width = "20em")
```

@@

```{r corpus-lda-model, cache = TRUE, include=FALSE}
municipal_lda <- LDA(municipal_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)

@@

```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}CAPTION THIS FIGURE"}
policy_top_terms <- policy_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

@@

```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}CAPTION THIS FIGURE"}

@@

Finally, we conduct topic modelling to examine the different topics found in the policy and academic corpora. We focus on the policy corpus, instead of individually assessing the municipal, school, and consortia documents, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario. To determine the number of discrete topics in each corpus, we use the _ldatuning_ package. We then use the `LDA` function from the _topicmodels_ package to estimate an LDA model for each group of documents. The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics. After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified. We experimented with the model by adjusting the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap. Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
